\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/abstract.tex
abstract nits

We study the extent and types of execution that can be performed in the
``speculative world'', and build tools that enable several computations to be
performed covertly. In particular, within speculative execution we are able to
decrypt memory using AES-NI instructions, and are able to interpret a custom
virtual machine language to perform arbitrary computation.
We also show how the trigger program
can be a pre-existing benign application already running on the system, and
demonstrate this concept with OpenSSL driven remotely by the attacker as our
trigger program.

@@

\speculake demonstrates a new kind of malware that evades existing reverse
engineering and binary analysis techniques. Because its true functionality can be
contained in seemingly unreachable dead code, and its control flow driven
externally by any other program running at the same time, \speculake poses a
novel threat to state-of-the-art malware analysis techniques.

>>>>

We study the extent and types of execution that can be performed
speculatively, and build tools that enable several computations to be
performed covertly. In particular, within speculative execution we are able to
decrypt memory using AES-NI instructions, and are able to interpret a custom
virtual machine language to perform arbitrary computation.
We also show how the trigger program
can be a pre-existing benign application already running on the system, and
demonstrate this concept with OpenSSL driven remotely by the attacker as our
trigger program.

@@

\speculake demonstrates a new kind of malware that evades existing reverse
engineering and binary analysis techniques. Because its true functionality is
contained in seemingly unreachable dead code, and its control flow driven
externally by potentially any other program running at the same time, \speculake poses a
novel threat to state-of-the-art malware analysis techniques.
